---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RStudioBackupPrefs

<!-- badges: start -->
[![R-CMD-check](https://github.com/Minh-AnhHuynh/RStudioBackupPrefs/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Minh-AnhHuynh/RStudioBackupPrefs/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of RStudioBackupPrefs is to provide an easy and online way to backup and restore your R Studio preferences.

## Installation

You can install the development version of RStudioBackupPrefs from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Minh-AnhHuynh/RStudioBackupPrefs")
```
Additionally I am fond of the `librarian` package, you can install with it:
```{r}
# install.packages("librarian") librarian::shelf() will install or load the
# package if already installed. You can queue up multiple package in one line.
librarian::shelf(Minh-AnhHuynh/RStudioBackupPrefs)
```



## Example

This is a basic example which shows you how to use the package:

```{r example}
# Backup your preferences
library(RStudioBackupPrefs)
start_backup_prefs(github_backup = TRUE)


# Import your preferences
start_import_prefs(pull_github = TRUE, clone_git = FALSE)

# Use clone_git = TRUE for first time usage
start_import_prefs(clone_git = TRUE)

```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

